On Optimality of Finite Element Integration

### 2015-12-28 TOMS_Paper/assembly.tex
Minor fixes.

\item If $\mathbb{S} = \emptyset$, jump to step (6). Otherwise apply, in order, the following rewrite rules (\textit{precondition}: \textit{action}):
\begin{enumerate}[label=(\Alph*)]
\item $\lbrace T^1, ..., T^n \rbrace \subset \mathbb{T}$ adjacent to $S$, $n > 1$: apply strategy (ii); $\mathbb{S} = \mathbb{S} \setminus \lbrace T^1, ..., T^n \rbrace$.\\ \textit{Note: strategy (ii) recasts the expression as $S (...T^0 + ... + ...T^n)$}. 
\item Only one terminal $T$ adjacent to $S$: apply strategy (ii) including one non-terminal symbol $S^{nt}$. $\mathbb{S} = \mathbb{S} \setminus \lbrace T, S^{nt} \rbrace$.
\item $\mathbb{T} = \emptyset$: take $S$ adjacent to $\lbrace S^1, ..., S^d \rbrace$ such that $d$ is maximum (i.e. $S$ is the vertex with highest degree in $\mathbb{G}$) and apply strategy (ii);  $\mathbb{S} = \mathbb{S} \setminus \lbrace S^1, ..., S^d \rbrace$.
\end{enumerate}
Go back to step (2).

>>>>

\item If $\mathbb{S} = \emptyset$, jump to step (6). Otherwise apply, in order, the following rewrite rules (\textit{precondition}: \textit{action}):
\begin{enumerate}[label=(\Alph*)]
\item $\lbrace T^1, ..., T^n \rbrace \subset \mathbb{T}$ adjacent to $S$, $n > 1$: apply strategy (ii); $\mathbb{S} = \mathbb{S} \setminus \lbrace T^1, ..., T^n \rbrace$.\\ \textit{Note: strategy (ii) recasts the expression as $S (...T^0 + ... + ...T^n)$}. 
\item Only one terminal $T$ adjacent to $S$: apply strategy (ii) including one non-terminal symbol $S^{nt}$. $\mathbb{S} = \mathbb{S} \setminus \lbrace T, S^{nt} \rbrace$.
\item $\mathbb{T} = \emptyset$: take $S$ with highest degree and apply strategy (ii).
\end{enumerate}
Go back to step (2).
